---
title: "EvanWB_Homework3"
author: "Evan Woelk Balzer"
date: "28/01/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


```{r cars}
summary(cars)
```

```{r }

```
#Useful functions#
resid(my.regression) gets you residuals
You can then plot them using hist()

Note that fitted values are those drawn from you regression line (which becomes abline)

When you plot residuals against fitted values, you want to see similar variation across the whole plot: homoscedasticity. If the scatterplot is all bunched on one end and expands as you change in X, you see that variation changes as X does: that's bad! (variance in Y changed as value of X changed)

gvla: a function that checks for the relationships in your data
gvlma(my.regression)


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
